\clearpage
\addcontentsline{toc}{chapter}{Bibliografia}
\begin{thebibliography}{9}

\bibitem{semantic-primer}Antoniou Grigorios, Harmelen Frank.
  \emph{A semantic web primer}.
  Cambridge MIT press, 2004.

\bibitem{working-ontologist}Dean Allemang, Jim Hendler.
  \emph{SEMANTIC WEB for the WORKING ONTOLOGIST}.
  Morgan Kaufmann, 2008.

\bibitem{xml-recomendation}W3C.
  \emph{Raccomandazioni del w3c relative a XML e alle tecnologie relative}.\\
  ``http://www.w3.org/TR/xml/'',\\
  ``http://www.w3.org/TR/xml-names/'',\\
  ``http://www.w3.org/TR/xmlschema-0/'',\\
  ``http://www.w3.org/TR/xmlschema-1/'',\\
  ``http://www.w3.org/TR/xmlschema-2/'',\\
  ``http://www.w3.org/TR/xslt/'',\\
  ``http://www.w3.org/TR/xpath/'',\\
  ``http://www.w3.org/TR/xsl/'',\\
  ``http://www.w3.org/TR/xml-infoset''.

\bibitem{rdf-recomendation}W3C.
  \emph{Raccomandazioni del w3c relative a RDF}.\\
  ``http://www.w3.org/TR/rdf-syntax-grammar/'',\\
  ``http://www.w3.org/TR/rdf-primer/'',\\
  ``http://www.w3.org/TR/rdf-concepts/'',\\
  ``http://www.w3.org/TR/rdf-syntax-grammar/'',\\
  ``http://www.w3.org/TR/rdf-mt/'',\\
  ``http://www.w3.org/TR/rdf-schema/'',\\
  ``http://www.w3.org/TR/rdf-testcases/''.

\bibitem{owl}W3C.
  \emph{Raccomandazioni del w3c relative a OWL}.\\
  ``http://www.w3.org/TR/owl-guide/'',\\
  ``http://www.w3.org/TR/owl-features/''.

\bibitem{skos}W3C.
  \emph{Raccomandazioni del w3c relative a SKOS}.\\
  ``http://www.w3.org/TR/skos-primer/'',\\
  ``http://www.w3.org/TR/skos-reference/'',\\
  ``http://www.w3.org/2004/02/skos/''.

\bibitem{foaf}D. Brickley, L. Miller.
  \emph{FOAF Vocabulary Specification}.\\
  ``http://xmlns.com/foaf/spec/''.

\bibitem{std66}T. Berners Lee, et al.
  \emph{STD 66, RFC 3986, Uniform Resource Identifier (URI): Generic
    Syntax}.\\
  ``http://tools.ietf.org/html/std66'', January 2005.

\bibitem{std68}D. Crocker, P. Overell.
  \emph{STD 68, RFC 5234, Augmented BNF for Syntax Specifications: ABNF}.\\
  ``http://tools.ietf.org/html/std68'', January 2008.

\bibitem{jqueryuilayout} \emph{jQuery UI Layout}.\\
  ``http://layout.jquery-dev.net/''

\bibitem{Cunningham2011a}Hamish Cunningham and Diana Maynard and Kalina Bontcheva and Valentin Tablan and Niraj Aswani and Ian Roberts and Genevieve Gorrell and Adam Funk and Angus Roberts and Danica Damljanovic and Thomas Heitz and Mark A. Greenwood and Horacio Saggion and Johann Petrak and Yaoyong Li and Wim Peters.
 \emph{Text Processing with GATE (Version 6)}. 2011.\\
 ``http://tinyurl.com/gatebook''

\bibitem{Appelt:1998:CPS:1119089.1119095}Appelt, Douglas E. and Onyshkevych, Boyan.
 \emph{The common pattern specification language}, 1998.

\bibitem{Cunningham2002}Hamish Cunningham and Diana Maynard and Kalina Bontcheva and Valentin Tablan.
\emph{GATE: A Framework and Graphical Development Environment for Robust NLP Tools and Applications}. 2002.

\end{thebibliography}
